---
title: "LIST disk use report"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: phs_logo_mono.png
    css: css_styles.css
date: "`r format(Sys.time(), '%d %b %Y')`"
---

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)
library(crosstalk)
library(DT)
library(utf8)

source("pre_process_and_wrangle.R")

```
# Notes and Overview {data-icon="fa-info-circle"}

## col {data-width=400}


### Notes {data-height=200}

* These interactive charts show disk space usage for the ``LIST_analytics`` drive.
* Hover over the chart for more information, including file paths and user names.
* <span style="color: red;">**NB:**</span> Users shown as only numbers (e.g. 3266) are no longer working for PHS. The relevant teams should look at these files to determine if they are still of value.
* This report is a large file. To avoid the irony of filling the drive with this report, please only open it from the email or store it temporarily while in use.
* If you have any questions or suggestions, please email them [here](mailto:sean.obrien@phs.scot).

<style>
div.phsblu50 { background-color:#E9D8D8; border-radius: 5px; padding: 18px; color: #A32E14}
</style>
<div class = "phsblu50">
Management Information only, not for onward distribution.
This report contains detailed information about the company file system and should not be distributed outside of PHS.
</div>



### Explanation {data-height=200}

Three additional pages can be selected at the top of the dashboard. They include: 

  1. <mark style="background-color: lightblue">**Users by team**</mark> shows total disk use by users within the team slected via the dropdown menu. The initial view shows disk use for all users.
  2. <mark style="background-color: lightblue">**Individual users**</mark> shows disk use by filename for the user selected via the dropdown menu. The initial view shows disk use of all files.
  3. <mark style="background-color: lightblue">**Data**</mark> allows you to view and filter the data and download as necessary (CSV). 
  
There is an issue with the drop down filters where selecting **(All)** does not remove the filter. To return to the the unfiltered chart, refresh the page.

## col

### Overview {data-height=100}

* Total disk use of ``LIST_analytics`` is shown below.
* The chart shows the disk use for each team, derived from filepaths as ``LIST_analytics\<team_name>\...``.


### 
```{r date}
valueBox(total_usage_str,
         paste0(used_capacity, " of ", total_capacity, " used."),
         color = "#867DCA")
```


###

```{r usage_by_group, echo=FALSE}
group_summary <- group_summary %>% mutate(pie_label=paste(group, total_use_str, sep = "\n"))

m <- list(
  l = 50,
  r = 50,
  b = 50,
  t = 50,
  pad = 0
)

fig <- group_summary %>% plot_ly(labels=~pie_label, values=~total_use)
fig <- fig %>% add_pie(hole=0.5, textinfo='label', hoverinfo='label+percent', textposition='inside')
fig <- fig %>% layout(title = list(text="", y=0.6, x=0.1),  showlegend = F, margin = m)
fig
```

# Users by team {data-icon="fa-chart-pie"}

## col {data-width=200}

### Choose Team
```{r input sidebar, echo=FALSE}
#put weird group names at the end
group_user_summary <- group_user_summary %>% arrange(grepl("^\\W", group), group)
group_user_summary <- group_user_summary %>% mutate(pie_label=paste(user, total_use_str, sep = "\n"))
group_user_summary_shared <- SharedData$new(group_user_summary)

filter_select("group", "Team Name", multiple=FALSE, group_user_summary_shared, ~group)
```

## col {data-width=800}

### User use in team
```{r users_in_group, echo=FALSE}
m <- list(
  l = -200,
  r = 0,
  b = 0,
  t = 0,
  pad = 0
)

fig <- group_user_summary_shared %>% plot_ly(labels = ~pie_label, values = ~total_use)
fig <- fig %>% add_pie(hole = 0.5, textposition='inside', hoverinfo="label")
fig <- fig %>% layout(showlegend = F, margins = m,
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

fig
```

# Individual users {data-icon="fa-chart-pie"}

## col {data-width=200}

### Choose User
```{r choose_user, echo=FALSE}
#custom label
files_by_user <- files_by_user %>% mutate(pie_label=paste(file_path, file_size_str, sep = "\n"))
files_by_user_shared <- SharedData$new(files_by_user)
filter_select("user", "User", multiple=FALSE, files_by_user_shared, ~user)
```

## col {data-width=800}

### File sizes for user
```{r files_by_user, echo=FALSE}
fig <- files_by_user_shared %>% plot_ly(labels = ~pie_label, values = ~file_size)
fig <- fig %>% add_pie(hole = 0.5, textposition='inside', hoverinfo="label")
fig <- fig %>% layout(showlegend = F,
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

fig
```

#Data {data-icon="fa-table"}
## col
###
```{r raw_data}
files_by_user <- files_by_user %>% select(user, group, file_size_str, file_path)
datatable(files_by_user, rownames=FALSE, filter="top", extensions = 'Buttons',
          colnames = c("User", "Team", "File Size", "File Path"),
          options=list(autoWidth = TRUE, buttons = c('csv'), paging = FALSE, dom = 'Bfrtip'),
          class = "display")

```

